Incentivizing Exploration with Unbiased Histories

### 2019-04-26 main.tex
Minor edit in the abstract.

\begin{abstract}
In a social learning setting, there is a set of actions, each of which has a payoff that depends on a hidden state of the world. A sequence of agents each chooses an action with the goal of maximizing payoff given estimates of the state of the world.  A disclosure policy tries to coordinate the choices of the agents by sending messages about the history of past actions. The goal of the disclosure policy is to minimize the regret of the action sequence \asedit{chosen by the agents. Prior work achieves much progress with disclosure policies that merely recommend an action to each user. However, all this work relies heavily on trust and rationality assumptions, which are standard and yet quite problematic in the context of recommendation systems.}

>>>>

\begin{abstract}
In a social learning setting, there is a set of actions, each of which has a payoff that depends on a hidden state of the world. A sequence of agents each chooses an action with the goal of maximizing payoff given estimates of the state of the world.  A disclosure policy tries to coordinate the choices of the agents by sending messages about the history of past actions. The goal of the disclosure policy is to minimize the regret of the action sequence \asedit{chosen by the agents. Prior work achieves much progress with disclosure policies that merely recommend an action to each user. However, all this work relies heavily on trust and rationality assumptions, standard in economic theory, yet quite problematic in the context of the motivating applications.}
